We kind of need a title

### 2020-02-28 methodology.tex
Added a paragraph on bias

    The survey will be distributed and filled out using Google Forms, as this allows us to reach a wider population and reduces the difficulty and commitment required to complete the survey. Email addresses, IP addresses, and other identifying information will not be collected. However, responses will be individual. Due to the nature of the questions, we do not believe this will create significant risk for the participants.

@@

>>>>

    The survey will be distributed and filled out using Google Forms, as this allows us to reach a wider population and reduces the difficulty and commitment required to complete the survey. Email addresses, IP addresses, and other identifying information will not be collected. However, responses will be individual. Due to the nature of the questions, we do not believe this will create significant risk for the participants. We intend to distribute the survey to nursing students.

@@

    While we will work to eliminate bias in the conclusions we draw from the data corpus, we acknowledge that our technical backgrounds may result in some bias that may harm the results of the study. We hope that application of the analysis methods listed above will go a long way to limiting the impact of bias.
